\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Peer Review 1}
\author{Benny Chen}
\date{}

\usepackage{color}
\usepackage{amsthm}
\usepackage{amssymb} 
\usepackage{amsmath}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

\begin{document}

\maketitle

\section*{Review 1 Houzhi(Steven) Hu}

This video talks about what a explosive eruption is and the effects of it. This video gives a general overview while also giving some statiscs and facts about the explosion. This video was engaging and gave a quick but concise overview of a volcanic eruption. There wasn't any graphics in the video however, some graphics would definitely help in showing the effects of the eruption along. Someone who has never heard of this topic would learn from this video. This video gave a great general overview of the topic which is more than that person knew from the begining and was engaging.

\section*{Review 2 Ethan Stella-Mackie}

This video was about how fossils are formed. This video was also engaging and concise. This video was also formatted good as it had a good introduction about the envoirment for fossil creation then talked more baout the process of fossil creation. This video also did not have any graphics. For this video, graphics would help in showing the process of fossil creation. I think someone who has never heard of this topic would definitely learn from this video. This video gave a great general but in depth overview of the topic.

\end{document}