\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Peer Review 2}
\author{Benny Chen}
\date{}

\usepackage{color}
\usepackage{amsthm}
\usepackage{amssymb} 
\usepackage{amsmath}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

\begin{document}

\maketitle

\section*{Review 1 - Our Soil is Dying}

The general overview of the video is about how soil is being lost overtime or dying. This video talks about some of the reasons this is happening and the effects of it. I found this video very engaging due to its production. The video has many visuals to show the viewer along with very nice transitions between the visuals, enhancing the viewers experince. Some raphics used were compaisons between soil along with graphics of the facts to enhance what the narrator is saying. I feel like someone would learn at general level of the topic. There should have been a better conclusion to the video to wrap everything back up. The video was very informative and I learned a lot from it. I would recommend this video to someone who wants to learn about soil and its importance.

\section*{Review 2 - Technofossil at UConn}

The general overview of this video is a example of a technofossil at UConn. This video talks specfically about the Jacobson Barn and how it is a technofossil and how future generations would be able to find it. This video was somewhat engaging due to the style of the video as someone is speaking directly to you. The visuals were not very engaging as it was just a picture of the barn. I feel like there would be more graphics to help the viewer along and better show the facts that she says. I feel like someone would learn at a general level of how the barn is a technofossil. I feel like there should have been more information about why the barn is a technofossil. 

\end{document}